The Early Eocene Climate Optimum reconstructed with Bayesian multi-proxy integration

### 2022-09-03 manuscript/manuscript.Rmd
Update manuscript.Rmd

In contrast, we put informative priors on the regression coefficients $A$, $K$, $M$ and $B$, based on physical principles and knowledge from the modern climate system. Specifically, we used the priors to express the following constraints and prior knowledge:
1) Predicted seawater surface temperatures is not allowed to be $<< -2^\circ C$, the freezing point of sea water.
2) Input of solar energy decreases from the tropics to the poles. Hence, the latitudinal temperature gradient is generally negative, i.e. temperature decreases with absolute latitude. This is achieved by constraining $K-A$ to be positive.
3) The steepness of the gradient is likely highest in mid-latitudes.
4) The 
a skew-normal prior on the lower asymptote $A$, with ...  . This constrains $A$ to not be $<< -2^\circ C$, which is the freezing point of sea water. We chose this distribution such that its mode is $~ 0^\circ C$, slightly higher than the modern...

>>>>

In contrast, we put informative priors on the regression coefficients $A$, $K$, $M$ and $B$, based on physical principles and knowledge from the modern climate system:
1) Predicted seawater surface temperatures is not allowed to be $<< -2^\circ C$, the freezing point of sea water.
2) Input of solar energy decreases from the tropics to the poles. Hence, the latitudinal temperature gradient is generally negative, i.e. temperature decreases with absolute latitude. This is achieved by constraining $K-A$ to be positive.
3) The steepness of the gradient is likely highest in mid-latitudes.
4) The 
a skew-normal prior on the lower asymptote $A$, with ...  . This constrains $A$ to not be $<< -2^\circ C$, which is the freezing point of sea water. We chose this distribution such that its mode is $~ 0^\circ C$, slightly higher than the modern...
